Testing the Relationship between Phenomenological Control related to Illusion Sensitivity

### 2025-05-01 paper/R1/manuscript.qmd
minor changes to manuscript

Participants will be presented with a consent form followed by demographic questions (gender, education level, age, and ethnicity). 
**Although these variables are not directly analyzed in the current study, they will be used to provide to provide a detailed and thorough description of the sample and maximizing data reusability.** 
**Participants will then be administered the PCS and the Illusion Game task (IG) in a counterbalanced order.**

@@

The PCS will contain several manipulation check indices to identify problematic participants. 
**The phenomenological control task consists of various auditory and visual exercises.**
**At the start of the task, participants first hear someone say "hello." They are then asked to choose from several options, including "Hello," "Goodbye," "How are you," and "Thank you".**
**Any participant who selects an option other than the correct one will be considered inattentive**
**In another exercise, participants receive the following instruction: “Open your eyes. You will see only two balls on the screen…just two balls”.**
**However, three differently coloured balls are actually displayed.**
**If participants select the option "no balls were shown", it indicates they failed to pay attention to both the auditory instructions and the visual stimuli.**
**Lastly, in another exercise, participants are asked to press the spacebar six times.**
**If they press it fewer than five times within the allotted time, it suggests a lack of attentiveness to the auditory instructions.**
**Participants will be excluded if they fail at least one of these checks.**
**Lastly, reliability of the PCS will be assessed by computing Cronbach's alpha [@cronbach1951coefficient].**

**To assess whether the illusions functioned as expected, stimuli will be categorized into three groups: Strong Illusion Strength & Incongruent, Mild Illusion Strength & Incongruent, and Congruent.**
**Two Bayesian t-tests will be conducted to assess differences in IES between the Congruent and Mild conditions, and between the Mild and Strong conditions.**
**Significant differences in these comparisons will provide evidence that the illusions functioned as intended.**

>>>>

Participants will be presented with a consent form followed by demographic questions (gender, education level, age, and ethnicity). 
**Although these variables are not directly analyzed in the current study, they will be used to provide a detailed and thorough description of the sample and maximizing data reusability.** 
**Participants will then be administered the PCS and the Illusion Game task (IG) in a counterbalanced order.**

@@

**The phenomenological control task will include several manipulation check indices to identify problematic participants.** 
**The task consists of various auditory and visual exercises; at the outset, participants hear a voice say “hello” and are asked to select the corresponding phrase from multiple options (e.g., “Hello,” “Goodbye,” “How are you,” “Thank you”).** 
**Selecting an incorrect response indicates inattention to auditory stimuli.** 
**In a subsequent exercise, participants are instructed: “Open your eyes. You will see only two balls on the screen… just two balls”.** 
**However, three differently coloured balls are displayed.** 
**If a participant selects the response “no balls were shown,” it suggests they failed to attend to both the auditory instruction and the visual stimuli.** 
**In another task, participants are instructed to press the spacebar six times.** 
**Pressing it fewer than five times within the allotted time indicates a failure to follow the auditory instructions.** 
**Participants who fail any one of these manipulation checks will be excluded from further analysis.** 
**Finally, reliability of the PCS will be assessed by computing Cronbach's alpha [@cronbach1951coefficient].**

**To assess whether the illusions functioned as expected, stimuli will be categorized into three groups: Strong Illusion Strength & Incongruent, Mild Illusion Strength & Incongruent, and Congruent.**
**Two Bayesian t-tests will be conducted to assess differences in IES between the Congruent and Mild conditions, and between the Mild and Strong conditions.**
**The IES is calculated by dividing the average correct RTs by the proportion of correct responses.**
**Significant differences in these comparisons will provide evidence that the illusions functioned as intended.**
